### 2023-03-22 discussion.qmd
update

## PARTUM LOUIS LEGENDRE

>>>>

## Continuous vertical sequestration

Using the CONVERSE approach, we have estimated that the global carbon sequestration (\> 100 years) flux by the BCP is 0.9-2.6 Pg C y$^{-1}$. This is 2-3 and 3-6 times larger than POC fluxes at, respectively, 1000 and 2000 m. CONVERSE sequestration flux estimates are also up to 4 times larger than those from studies assuming that sequestration occurs below a fixed reference depth [@Honjo2008-kn, @Guidi2015-sj; @Henson2012-ck]. Here below, I highlight some key points and ways to improve further our estimations.

### Marine carbon dioxide removal strategies

The goal of marine carbon dioxide removal (mCDR) strategies [@Boyd2023-xf] is the removal of excess CO$_{2}$ from the atmosphere and the sequestration of carbon away from the atmosphere for a given time period [@National_Academies_of_Sciences2022-ah]. Several mCDR strategies have been proposed such as increasing alkalinity to enhance the chemical uptake of atmospheric CO$_{2}$ [@Hartmann2023-vk], increasing the photosynthetic uptake of atmospheric CO$_{2}$ with iron and macronutrients fertilization [@Blain2007-ws] or directly injecting CO$_{2}$ into the deep ocean [@Siegel2021-oz].

We have seen with CONVERSE that carbon sequestration occurs on the whole water column and that using a fixed reference depth would likely miss the bulk of sequestration. Therefore, the evaluation of future mCDR strategies using biologically-driven carbon sequestration fluxes should be estimated over the whole water column.

### Particle injection pumps

Our study on the sequestration flux by the BCP also shows that the contribution of the vertical migration and mixing pumps contribute at least to 20-31% of the sequestration flux by the BCP.

dire qu'il faut améliorer la physical et la VMP (diel et saisonnière) -\> mettre le paquet sur ARGO (et les gliders pour la physical) + papier d'Hervé de 2021. + préciser qye la migration saisonnire est sous-évaluée.

### 2023-03-22 index.qmd
update

I hope you will enjoy it and no, I won't tweet about it. -->
```

>>>>

I hope you will enjoy it.
```
```{=html}
<!-- This thesis started in probably the worst conditions possible but here it is, it is finally over. Why such a relief? I have my personal case which I really do not wish to anyone. I hope things have changed but when I reached for help at my university, I quickly understood that I had to shut my mouth. Wait, it is not that I have understood, I was told out loud that if I kept pushing, I was going to be laid off. I was not, do you want to know why?

#Respect, I got so many emails about that, it is hilarious. Instead of tweeting, perhaps some people should listen and act. For what , academia is a centralized institution without safeguards. The same person can be faculty president, lab chief, group master and mental health hotline (true story) at the same time. The only difference with politics is that you do not get more money in your pocket by cumulating

Here it is, the product of my resilience. I have to say that I am wrapping this up in a good shape, both mentally and physically. I am a lucky one. Some people are surprised that some of us do not want to pursue a career in academia. Just wait for it.

I truly wish good luck to all current and future PhD students and I hope they can have the strength to say no when they need to. Trust me, it will be useful. -->
```

### 2023-03-22 merci.qmd
update discussion
update

@@

@@

@@

>>>>

merci antoine poteau et fabrizio depuis 2018

merci a chatGPT pour la cover, elle n'est pas top mais j'avais la flemme, c'était suffisant

@@

Mathieu de m'avoir accueillu sur ton divan à Bx quand j'en avais besoin

@@

ma maman qui a accepté de m'héberger dans une période incertaine même si elle connait mon besoin d'indépendance.

@@

Go Belgium and go Mons
